The impact of gas bulk rotation on the Lyman $\alpha$ line

### 2014-09-10 paper/referee-reply.tex

Best regards, \\

The Authors\\

\section*{Minor Comments}

{\bf The color bar in Fig 2 and 3 has no units. Indeed, there is only a factor of $2$ in “flux” between a
red and a green pixel, so the broadening of the line compensates the change in color with $\theta$. I still
believe that you should comment on this in the text, because the visual impression is really that
there are less photons escaping along the equator than along the rotational axis. Especially when
you look at the top right panel.}\\

Thank you very for notest this, we put the right units and also we comment on that in the text.\\

{\bf could you add the intrinsic spectra for uniform sources on Fig4 ? And maybe add a fig5 which
would be the same as Fig4, but for $\theta = 0$? To illustrate the 2 extreme cases.}\\

About Fig 4. we add the intrinsic spectra, and we add an aditional figure showing the case $\theta=0$ to illustrate the 2 extremes
cases. When we add the intrinsic spectra we cut the plot to the heigh of the rotation spectra because the intrinsic spetra is to high 
and the details of the rotation spectra can not be apreciated.\\

{\bf About the directionallity of the escaping photons, why did you select only photons with $0 < \varphi < \pi/2$? Did you then normalise the blue and green curves to sample the same number of photons ? Now that I understood that Lya transfer in solid-body rotating cloud proceeds like in a static medium, until projection in an external, non-rotating frame, the only expected trend should be with optical depth, indeed. These curves show $I(\mu)$ that you discuss in the appendix, right ? It seems that the regimes that you investigated are not yet enough optically thick so that $I(\mu) = \propto \mu$. Maybe you can show these plots on the appendix, to illustrate that the analytic solution becomes better in veryoptically thick regimes.}\\

### 2014-09-10 paper/referee-reply.tex

The Authors\\

\section*{Minor Comments}

{\bf The color bar in Fig 2 and 3 has no units. Indeed, there is only a factor of $2$ in “flux” between a
red and a green pixel, so the broadening of the line compensates the change in color with $\theta$. I still
believe that you should comment on this in the text, because the visual impression is really that
there are less photons escaping along the equator than along the rotational axis. Especially when
you look at the top right panel.}\\

Thank you very for noticing this. We have put the right units and also we have added a comment in the text.\\

@@

{\bf could you add the intrinsic spectra for uniform sources on Fig4 ? And maybe add a fig5 which
would be the same as Fig4, but for $\theta = 0$? To illustrate the 2 extreme cases.}\\

We have followed your advice and modified figure 4 and 5 accordingly.\\

@@

{\bf About the directionallity of the escaping photons, why did you select only photons with $0 < \varphi < \pi/2$? Did you then normalise the blue and green curves to sample the same number of photons ? Now that I understood that Lya transfer in solid-body rotating cloud proceeds like in a static medium, until projection in an external, non-rotating frame, the only expected trend should be with optical depth, indeed. These curves show $I(\mu)$ that you discuss in the appendix, right ? It seems that the regimes that you investigated are not yet enough optically thick so that $I(\mu) = \propto \mu$. Maybe you can show these plots on the appendix, to illustrate that the analytic solution becomes better in veryoptically thick regimes.}\\

We did not limit the selection to $0 < \varphi < \pi/2$. The outgoing
photons close to the surface are in that range, where $\varphi$
describes the angle with respect to the normal to the surface.  The
curves have the same normalization in each plot.

### 2014-09-10 paper/ms.tex
paper updtaed
Minor changes
minor update caption fig 10

The main results of this paper are summarized in Fig.
\ref{fig:CentralSpec} and \ref{fig:HomSpec}. 
They show 2D histograms of the escape frequency $x$ and outgoing angle
$\theta$ parametrized by $|\mu|$. 
Taking into account only photons photons around a value
of $|\mu|$ gives us the emission detected by an observer located at an
angle $\theta$ with respect to the rotation axis. 
We have verified that the solutions are indeed symmetric with respect
to $\mu=0$.

@@

\begin{figure*}
\begin{center}
    \includegraphics[width=0.45\textwidth]{f12.pdf}
    \includegraphics[width=0.45\textwidth]{f13.pdf}
\end{center}
\caption{Logarithm of the average number of scatterings as function of
  $\mu$ (left) and the maximum rotational velocity $V_{\rm
max}$ (right). The left panel shows the behaviour for $\tau=10^{5}$ and
  $V_{max}=300$\kms as a function of $\left|\cos\theta\right|$. In the
  right panel the continous (dashed) lines represent the results for
  the central (homogeneous) model. The independence of $N_{\rm scatt}$ with $\mu$ and $V_{\rm max}$ is
  present in all models.  
\label{fig:Nscatt} }
\end{figure*}

>>>>

The main results of this paper are summarized in Fig.
\ref{fig:CentralSpec} and \ref{fig:HomSpec}. 
They show 2D histograms of the escape frequency $x$ and outgoing angle
$\theta$ parametrized by $|\mu|$. 
Taking into account only photons photons around a value
of $|\mu|$ gives us the emission detected by an observer located at an
angle $\theta$ with respect to the rotation axis. 
We have verified that the solutions are indeed symmetric with respect
to $\mu=0$. We have also verified that the total flux is the same for all $\mu$.

@@

\begin{figure*}
\begin{center}
    \includegraphics[width=0.45\textwidth]{f12.pdf}
    \includegraphics[width=0.45\textwidth]{f13.pdf}
\end{center}
\caption{2D histogram of the logarithm of the average number of scatterings as function of $\mu$ (left) and the maximum rotational velocity $V_{\rm
max}$ (right). The left panel shows the behaviour for $\tau=10^{5}$ and
  $V_{max}=300$\kms as a function of $\left|\cos\theta\right|$, the color indicates the number of photons per bin. In the
  right panel the continous (dashed) lines represent the results for
  the central (homogeneous) model. The independence of $N_{\rm scatt}$ with $\mu$ and $V_{\rm max}$ is
  present in all models.  
\label{fig:Nscatt} }
\end{figure*}
